---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# IRsupportR

<!-- badges: start -->

<!-- badges: end -->

The objective of this package is to compile and evaluate historic water quality data to verify if the data supports impairments attributed to toxics. In order to accomplish this objective, data from various datasets are compiled and processed into one consistent dataset for comparing to numeric water quality criteria. Exceedances of the water quality criteria are determined and categorization reevaluation decisions are proposed based on the implementation of an approved decision logic. 

## Installation

You can install the development version of IRsupportR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("LimnoTech/IRsupportR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(IRsupportR)
## basic example code
```


